Designing Types for R, Empirically

### 2020-09-11 paper/main.tex
layout for follow-up discussion on kaggle, other patterns, and revdeps types. will aim to have draft prose/bullets in by EOD tmr

Turning our attention now to arguments, we found that only
\PROPARGSFAILINGASSERTS of parameters failed.
Table~\ref{tbl:fail-breakdown-0} showed the runtime occurrences, but that
data alone does not tell the full story, as some failures may be
overrepresented if e.g. a failing contract assertion was in a loop.  We were
interested in knowing for each of the most common violations in
Table~\ref{tbl:fail-breakdown-0}, how many different arguments had that
type, and how many of those exhibited the contract failure in question.
Table~\ref{tbl:fail-breakdown-1} breaks down the failed assertions by type,
folding away multiple identical failed contract assertions for the same
parameter position.  The first row of this table reads: a value of type
\VEC\dbl was passed to 15 different function parameters expecting a
\CLASS{\texttt{matrix}}, of which there are 1394 in total: 1\% of
\CLASS{\texttt{matrix}}-typed parameters were passed \VEC\dbl values.

@@

\AT{Do we want to expand on this evaluation?
Or just expand in a more general section later.}

 %
 %
 \subsubsection{Kaggle}

@@

>>>>

Turning our attention now to arguments, we found that only
\PROPARGSFAILINGASSERTS of parameters failed.
Table~\ref{tbl:fail-breakdown-0} showed the runtime occurrences, but that
data alone does not tell the full story, as some failures may be
overrepresented if, e.g., a failing contract assertion was in a loop.  We were
interested in knowing for each of the most common violations in
Table~\ref{tbl:fail-breakdown-0}, how many different arguments had that
type, and how many of those exhibited the contract failure in question.
Table~\ref{tbl:fail-breakdown-1} breaks down the failed assertions by type,
folding away multiple identical failed contract assertions for the same
parameter position.  The first row of this table reads: a value of type
\VEC\dbl was passed to 15 different function parameters expecting a
\CLASS{\texttt{matrix}}, of which there are 1394 in total: 1\% of
\CLASS{\texttt{matrix}}-typed parameters were passed \VEC\dbl values.

@@

 %
 %
 \subsubsection{Other Observations}

 \AT{Kinds of failures: vectors passed to scalars, wrong things passed to classes, nulls passed to non-nullable arguments.}

 We observed a number of other interesting patterns in the contract assertion failure data.

 First, we were curious about how many \null-typed values flowed into non-nullable arguments.
 We found that \AT{fill in numbers}.
 Of these, there were three main kinds of ``type errors''.

 \begin{itemize}
   \item One kind of type error occurs when an argument with a {\tt NULL} default value is not given a value by the programmer.
   In testing, the programmer only tested the function by passing values to these null-by-default arguments.
   \AT{Check correlation with coverage.}

   \item Another kind of type error occurs when {\tt NULL} is passed to an argument which is not expected to be {\tt NULL}, but that does not cause an error.
   One example is \AT{see as.integer example}.

   \item Finally, in some cases the {\tt NULL}s resulted in errors, either unhandled or handled by a check and a conditional.
 \end{itemize}

 Next, we were curious about how often vectors were passed to arguments expecting scalars.
 We found \AT{finish analysis, numbers}.
 Besides an outright error, this kind of contract assertion failure might indicate that a function was not well-tested, in that it was only ever tested with unit-length vectors being passed to an argument which is intended to have a vector type.
 Further, these errors may reveal functions that were not designed with a vector-typed argument in mind, but can in fact handle vectors of values (in R, most functions that can accept scalars can also accept vectors).
 %
 %
 \subsubsection{Kaggle}

@@

 \AT{Discuss how things match up between Kaggle and revdeps.}
